Workflow Part II: for inverse root modeling and post-processing

### 2020-11-12 Readme.Rmd
updated title and description

---
title: "Workflow"
author: "Rutuja Chitra-Tarak"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
subtitle: Hydraulically-vulnerable trees survive on deep-water access during droughts
  in a tropical forest
---

@@

- Soil Water Potentials
- VPD-GPP relationship
- Leaf vulnerability curves
- LAI seasonality
- Hydraulic traits

>>>>

---
title: "Workflow Part II: for inverse root modeling and post-processing"
author: "Rutuja Chitra-Tarak"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
subtitle: Hydraulically-vulnerable trees survive on deep-water access during droughts
  in a tropical forest
---

@@

- Soil Water Potentials (outputs from ELM-FATES)
- VPD-GPP relationship
- Leaf vulnerability curves
- LAI seasonality
- Hydraulic traits
